\documentclass[11pt,a4paper]{article}

% --- Packages ---
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs} % For professional tables
\usepackage{listings} % For code snippets
\usepackage{xcolor}

% --- Python Code Styling ---
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\lstset{
    language=Python,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue},
    commentstyle=\color{codegreen},
    stringstyle=\color{orange},
    breaklines=true,
    numbers=left,
    numberstyle=\tiny\color{codegray},
    frame=single
}

% --- Title Information ---
\title{JC1503: Object-Oriented Programming \\ \huge Group Project: Personal Data System}
\author{Group [Insert Group Number]}
\date{\today}

\begin{document}

\maketitle

% --- Requirement: Individual Contributions on First Page ---
\section*{Individual Contributions}
\begin{table}[h]
    \centering
    \begin{tabular}{lp{6cm}p{5cm}}
        \toprule
        \textbf{Member Name} & \textbf{Responsibilities} & \textbf{Technical Implementation} \\
        \midrule
        Student 1 & e.g., System Architecture & e.g., BST, Inheritance structure \\
        Student 2 & e.g., Data Persistence & e.g., File I/O, Hash Table \\
        Student 3 & e.g., Testing \& Debugging & e.g., Unit tests, Custom Exceptions \\
        Student 4 & e.g., UI \& Operations & e.g., Search/Delete logic \\
        \bottomrule
    \end{tabular}
    \caption{Summary of individual member responsibilities.}
\end{table}

\vfill
\begin{center}
    \textit{Note: Total report length must not exceed 10 pages.}
\end{center}
\newpage

% --- Section 1: Problem and System Design ---
\section{Problem and System Design}
\label{sec:problem_design}
% Requirement: Real-world situation, main entities, and system structure.

\subsection{Application Domain}
Describe your chosen scenario (e.g., Hospital Records, Finance Tracker) and the real-world problem it manages.

\subsection{System Architecture}
Explain the overall structure and how the user interacts with the application. Justify why this is a coherent system rather than a script.

% --- Section 2: Technical Design ---
\section{Technical Design}
\label{sec:technical_design}
% Requirement: OOP structure, Data Structures, and Algorithms.

\subsection{Object-Oriented Modelling}
Explain your use of:
\begin{itemize}
    \item \textbf{Inheritance and Abstraction:} (e.g., Base classes for records).
    \item \textbf{Composition:} How objects relate to one another.
    \item \textbf{Encapsulation \& Polymorphism:}.
\end{itemize}

\subsection{Data Structures and Algorithms}
Justify the use of the following required structures :
\begin{itemize}
    \item \textbf{Linear Structures:} Doubly Linked List, Stack, and Queue.
    \item \textbf{Non-Linear Structures:} Tree and Binary Search Tree (BST) including recursive traversal.
    \item \textbf{Mapping:} Hash Table / Map structure.
\end{itemize}

\subsection{Efficiency and Complexity}
Discuss the algorithmic reasoning and complexity considerations for your search/query operations.

% --- Section 3: Development and Testing ---
\section{Development and Testing}
\label{sec:dev_testing}
% Requirement: Evolution, problems encountered, and testing evidence.

\subsection{Iterative Development}
Describe how the system evolved from the initial dataset generation to the final persistent state.

\subsection{Problem Solving}
Detail at least one significant technical problem encountered, how you diagnosed it, and the fix applied.

\subsection{Testing Strategy}
Provide evidence of:
\begin{itemize}
    \item \textbf{Unit Testing:} Individual methods.
    \item \textbf{System Testing:} End-to-end functionality.
\end{itemize}

% --- Section 4: Reflection ---
\section{Reflection}
\label{sec:reflection}
% Requirement: Successes, limitations, and learning outcomes.

\subsection{Critical Assessment}
What aspects of the design work well? What are the current limitations (e.g., scalability of specific data structures)?

\subsection{Future Improvements}
If you had more time, what would you change or extend?

\subsection{Learning Outcomes}
Reflect on what the group learned about software design and OOP principles.

\end{document}